---
title: "mark_art package description"
author: "XC"
date: "1/27/2022"
output: html_document
---

## Usage and description
```{r, eval=FALSE}

make_art()
```

This function make_art is for users to create random pictures of scatter plots. ggplot2 need to be installed and loaded before using make_art. The argument taken is a random number, which makes the graph reproducible. This argument is optional. 

## An example output
```{r, eval=TRUE, echo=FALSE}
library(ggplot2)
make_art <- function(seed){
  if(missing(seed)){
    x <- c(rnorm(500, 0, 1))
    y <- c(rnorm(500, 2, 3))
    z <- c(rep("a", 150), rep("b", 150), rep("c", 200))
    df <- data.frame(x, y, z)
    ggplot(data = df, aes(x, y)) + geom_point(aes(color = z)) +
      theme_bw()+ scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))
  }else{
    set.seed(seed)
    x <- c(rnorm(500, 0, 1))
    y <- c(rnorm(500, 2, 3))
    z <- c(rep("a", 150), rep("b", 150), rep("c", 200))
    df <- data.frame(x, y, z)
    ggplot(data = df, aes(x, y)) + geom_point(aes(color = z)) +
      theme_bw()+ scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))
  }
}
make_art(1)
